\large{\bf Looking forwards and backwards through locally regulated populations }

### 2022-04-07 forwards-and-backwards.tex
Update on Overleaf.

\begin{definition}[Model parameterization and assumptions]
    \label{def:model_setup}
    For each $\theta \ge 0$,
    let $\left(\eta^\theta(t)\right)_{t \ge 0}$
    be the continuous-time measure-valued Markov process described above
    with birth rates, establishment probabilities, and death rates
    determined as follows.
    Suppose $\gamma(x, m)$, $r(x, m)$, and $F(x, m)$
    are bounded, uniformly continuous functions
    from $\IR^d \times \IR_{\ge 0}$ to $\IR_{\ge 0}$.
    Furthermore, suppose $r$ takes values in $[0, 1]$
    and has uniformly bounded second derivatives,
    and that $(x, m) \mapsto m^2 \gamma(x, m)$ is unformly bounded.
    Fix nonnegative values $\epsilon_r$, $\epsilon_\gamma$, and $\epsilon_F$,
    with $\epsilon_r < \epsilon_\gamma - 1/\theta$.
    Suppose $F: \IR^d \times \IR_{\ge 0} \to \IR$ is bounded and uniformly continous
    and define
    \begin{align}
        \mu(x, \eta)
        =
        r(x, \smooth{r} \eta^{\theta}(x))
        \gamma(\smooth{\gamma} \eta^{\theta}(x))
        - \frac{1}{\theta}
        F(x, \smooth{F} \eta^{\theta}(x)) .
    \end{align}
    Let $N$ be a positive number determined by $\theta$.
    When the state of the process is $\eta$,
    offspring of mass $1/N$ are produced at location $x$
    with rate $\theta \gamma(x, \smooth{\gamma} \eta^{\theta}(x)) N \eta^{\theta}_s(dx)$
    and adults die at location $x$ with rate $\theta \mu(x, \eta) N \eta^{\theta}_s(dx)$,
    (i.e., at rates $\theta \gamma$ and $\theta \mu$ per capita respectively).
    Offspring disperse to a location offset from the parent's location
    by an independent Gaussian with mean $\meanq/\theta$
    and covariance matrix $\covq / \theta$;
    an offspring at $x$ establishes instantaneously
    with probability $r(x, \smooth{r} \eta^{\theta}(x))$, or else dies.
\end{definition}

@@

\paragraph{Remark:}
An equivalent way to describe the model
would be to say that an individual at $x$ gives birth at rate
$$
    \gamma(x, \smooth{\gamma} \eta^{\theta}(x))
    \int r(x, \smooth{r} \eta^{\theta}(y)) q(x, dy) ,
$$
and that offspring disperse according to the kernel
$$
    q_\theta^\mathfrak{m}(x, dy)
    :=
    \frac{
        r(y, \smooth{r} \eta^{\theta}(y)) q_\theta(x, dy)
    }{
        \int r(x, \smooth{r} \eta(z)) q_\theta(x, dz)
    } .
$$
Clearly, the random walk driven by this dispersal kernel
should be biased towards regions of higher establishment probability.
For comparison to future results,
it is interesting to write down the limiting generator:
\begin{align*}
    \lim_{\theta \to \infty}
    \theta \int (f(y) - f(x)) q_\theta^\mathfrak{m}(x, dy)
    &=
    \frac{
        \DG\left[ f(\cdot) r(\cdot, \smooth{r} \eta(\cdot)) \right](x)
        - 
        f(\cdot) \DG\left[ r(\cdot, \smooth{r} \eta(\cdot)) \right](x)
    }{
        r(x, \smooth{r} \eta^{\theta}(x))
    } .
\end{align*}
In the simplest case of unbiased, isotropic dispersal,
$\meanq = 0$ and $\covq = I$, so $\DG = \Delta$,
and this is equal to
\begin{align*}
    \Delta f(x) + 2 \grad f(x) \cdot \grad \log r(\cdot, \smooth{r} \eta(\cdot))(x) .
\end{align*}
However, we will see that following a lineage back through the population
has a different behavior yet again.

@@

    The sequence of stochastic processes
    $(\eta^\theta_t)_{t \geq 0}$
    converges along subsequences in distribution as $\theta \to \infty$
    to a measure-valued process $(\eta_t)_{t \geq 0}$
    which satisfies that, for every $f:\mathbb{R}^d \rightarrow \mathbb{R}$,
    \begin{align} \label{eqn:mgale_problem}
        M_t
        &:=
        \langle f(x), \eta_t(dx) \rangle
        -
        \langle f(x), \eta_0(dx) \rangle
        \\ & \qquad
        -
        \int_0^t \big\langle
            \gamma(x, \smooth{\gamma} \eta^{\theta}_{s}(x))
            \mathcal{B}\left(
                f(\cdot) r(\cdot, \smooth{r} \eta^{\theta}_{s}(\cdot))
            \right)(x)
            +
            f(x)
            F(x, \smooth{F} \eta^{\theta}_{s}(x)),
            \eta^{\theta}_{s}(dx)
        \big\rangle ds,
    \end{align}
    is a martingale.
    The quadratic variation of $M_t$ is given by 
    \begin{align} \label{eqn:mgale_variation}
        [ M ]_t
        =
        \delta
        \int_0^t
        \big\langle
            \gamma\left( x, \smooth{\gamma} \eta^{\theta}_{s}(x) \right)
            r\left(x, \smooth{r} \eta^{\theta}_{s}(x) \right)
            f^2(x),
            \eta^{\theta}_{s} (dx)
        \big\rangle ds. 
    \end{align}
    In other words, the limit is a measure-valued process with non-local interactions.
    Furthermore, if $\delta = 0$ the limit is deterministic.
\end{theorem}

@@

We now write down the generator of
the scaled population model with levels where 
$\lambda$ is the scaling factor of the mass of an individual,
$\theta(\lambda)$ is the scaling factor for time,
and the level of an individual particle must be in $[0,\lambda]$.
Recall that we only track the adult population; maturity, if achieved, is instantaneous.
Furthermore, at rate $\theta\gamma(x, \eta)$,
a parent gives birth to a single juvenile offspring.

We should consider an initial population of $O(\lambda)$ many particles with levels
uniformly distributed between $[0, \lambda]$.
We write $(\xi^{\theta, \lambda}(t))_{t \geq 0}$
for our population at the $\theta$-th stage of rescaling.
To recover the scaling in \S\ref{sec: Model and main results},
we scale the empirical distribution of particles with a factor of $1/\lambda$,
so we write
$$\eta^{\theta, \lambda}_t:=\frac{1}{\lambda}\xi^{\theta, \lambda}_t(dx \times [0,\lambda])=
\frac{1}{\lambda}\sum\limits_{\substack{(X(t),U(t))\in \xi \\ U(t) < \lambda}} \delta_{X(t)}.$$ 
From here onwards,
we write $\xi$ to be the particle systems with levels,
while $\eta$ is the normalised empirical distribution.
An individual in the spatial population $\eta$ living at spatial location $x$
produces one adult offspring at rate $\theta\gamma^{\mathfrak{m}}_{\theta}(x, \eta)$, where
$$\gamma^{\mathfrak{m}}_{\theta}(x,\eta)=\gamma(x,\eta) \int r (y, \eta)q_\theta(x,dy).$$

The location of this offspring is given by
the distribution 
\[ q^{\mathfrak{m}}_\theta(x,\eta,dy) = \frac{r(y,\eta) q_{\theta}(x,dy)}{\int_{\mathbb{R}^d} r(y,\eta) q_{\theta}(x,dy)}. \]

In the lookdown version of our model,
the individual $(x,u)\in \xi^{\theta, \lambda}$
gives birth to an offspring at rate 
$2(\lambda-u)\lambda^{-1}\theta \gamma^{\mathfrak{m}}_{\theta}(x, \eta)$. 
(Averaging over the distribution of the
level $u$,
we recover $\theta \gamma^{\mathfrak{m}}_{\theta}(x, \eta)$.)

@@

Evidently this mechanism increases the proportion
of individuals with higher levels.
To restore the property that,
conditional on $\eta$,
the intensity of levels is conditionally uniform,
we impose that 
the level associated with $(x,u)\in\eta$
evolves according to the differential equation
$$\dot{v}= \theta \gamma^{\mathfrak{m}}_{\theta}(x, \eta) 
\left\{\lambda^{-1}(\lambda -v)^{2}
-(\lambda -v)\right\}.$$

See~\cite{etheridge/kurtz:2018}, Section~3.4 for a detailed explanation.
In order to incorporate death,
the level of the individual $(x,u)\in \eta$ 
moves upwards at an additional rate
$\theta \mu(x,\eta)$
(on reaching level $\lambda$
an individual is deemed to have died).
Overall, we assume that
the level associated with $(x,u)\in\eta$
evolves according to
$$\dot{u}= \theta \gamma^{\mathfrak{m}}_{\theta}(x, \eta) 
\left\{\lambda^{-1}(\lambda -u)^{2}
-(\lambda -u)\right\}+\theta \mu(x,\eta)u.$$
We shall write 
$$b_{\theta, \lambda}(x,\eta):=\theta\big\{\gamma^{\mathfrak{m}}_{\theta}(x,\eta)
-\mu(x,\eta)\big\}.$$
Note that this quantity captures
the deviation from criticality
in the branching mechanism.
In this notation,
the differential equation 
governing the level of the individual $(x,u)\in\eta$ is
\begin{align}
\dot{u}&=\lambda \theta \gamma^{\mathfrak{m}}_{\theta}(x,\eta) 
\left\{\left(1-\frac{u}{\lambda}\right)^{2}
-1 +2\frac{u}{\lambda}\right\} -b_{\theta, \lambda}(x,\eta)u \nonumber \\
&=\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\eta) u^2 -b_{\theta, \lambda}(x,\eta)u. \label{differential equation for level}
\end{align}
In this setting, the generator of our model
acting on the test functions $f(\eta)=\prod_{(x,u) \in \eta}g(x,u)$
satisfies
%We assume that  locations in ${\mathbb{ R}}^d$.

\begin{eqnarray}\label{Generator of prelimit simplest model}
&&A_{\theta, \lambda}f(\eta ) \nonumber \\
&&\quad =f(\eta )\,\sum_{(x,u)\in\eta}\,2\lambda^{-1}\theta \gamma^{\mathfrak{m}}_{\theta}(x, \eta)
\int_u^{
\lambda}\Bigg(\frac 12\frac {\int_{\mathbb{R}^d}g(y,u)q^{\mathfrak{m}}_\theta(x,\eta,d
y)g(x,v_1)}{g(x,u)} \label{multgen3}\\
&&\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad
+\frac 12\int_{\mathbb{R}^d}g(y,v_1)q^{\mathfrak{m}}_\theta(x,\eta ,dy)-
1\Bigg)dv_1\nonumber\\
&&\quad \quad +f(\eta )\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\eta) u^2 -b_{\theta, \lambda}(x,\eta)u\right)\frac {\partial_u g(x,u)}{g(x,u)}\nonumber\\
&&\quad =f(\eta )\,\sum_{(x,u)\in\eta}\,2 \gamma^{\mathfrak{m}}_{\theta}(x, \eta)\lambda^{-1}\int_u^{
\lambda}\Bigg(\frac 12\frac {\theta\int_{\mathbb{R}^d}(g(y,u)-g(x,u))q^{\mathfrak{m}}_\theta(x,\eta,dy)g(x,v_1)}{g(x,u)}\non\\
&&\qquad\qquad\qquad\qquad\qquad\qquad\qquad +\theta\int_{\mathbb{R}^d}\left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_\theta(x,\eta,dy)\Bigg)dv_1\nonumber\\
&&\qquad\qquad
+f(\eta )\sum_{(x,u)\in\eta}\,\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\eta) u^2 -b_{\theta, \lambda}(x,\eta)u\right)\frac {\partial_u g(x,u)}{g(x,u)}.\nonumber
\end{eqnarray}
The two terms under the integral correspond, respectively,
to the parent being assigned a level other than $u$,
and being reallocated to the level $u$
during a birth event.
In the first case, the parent at location $x$,
which had level $u$ before the event,
moves to level $v_1$,
and the child is inserted at level $u$
and location $y$;
in the second the parent retains its level,
and offspring is inserted at level $v_1$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{Scaling of the Pre-limit}

We also let $\lambda$ takes on the role of $N$
in \S \ref{sec: Model and main results},
i.e. each individual has mass $1/\lambda$
in the scaling limit.
Time is once again scaled by $\theta$
and local interaction radius by $\varepsilon_{\gamma}$ and $\varepsilon_{r}$.

As in Definition \ref{Def: Rescaled Models},
the rates $\gamma,r, \mu_{\theta}$
in our re-scaled lookdown models 
depend on the local density of $\eta$
through mollifications with 
$\varrho_{\gamma}, \varrho_{r}$ and $\varrho_{F}$.
We will now make our re-scaled lookdown model explicit.

\begin{definition}[Martingale Problem Characterisation]
\label{Def: Rescaled Lookdown Models}
Let the coefficients $\gamma, \mu, r$ satisfy the conditions highlighted in Definition \ref{Def: Rescaled Models} and let $\varrho_{\varepsilon}$ be the kernel defined in Definition \ref{Defn: Kernel and Convolution}. We define the following terms:
\begin{align*}
\gamma^{\mathfrak{m}}_{\varepsilon,\theta}(x, \eta):=&~\gamma(x, \varrho_{\varepsilon}*\eta^{\theta}(x)) \int r(y, \varrho_{\varepsilon}*\eta^{\theta}(y))q_{\theta}(x,dy),\\
 q^{\mathfrak{m}}_{\varepsilon, \theta}(x,\eta,dy) :=&~ \frac{r(y,\varrho_{\epsilon}*\eta^{\theta}(y)) q_{\theta}(x,dy)}{\int_{\mathbb{R}^d} r(y,\varrho_{\epsilon}*\eta^{\theta}(y)) q_{\theta}(x,dy)},\\
b_{\varepsilon, \theta, \lambda}(x, \eta):=&~ \theta \bigg\{ \gamma(x, \varrho_{\varepsilon}*\eta^{\theta}(x)) \int r(y, \varrho_{\varepsilon}*\eta^{\theta}(y))q_{\theta}(x,dy)-\mu_{\theta}(x, \varrho_{\varepsilon}*\eta^{\theta}(x)) \bigg\}
\end{align*}
At the $\lambda$-stage of re-scaling, our test measures $\eta$ takes value in $\mathcal{M}_F(\mathbb{R}^d \times [0,\lambda])$, the set of finite measures on $\mathbb{R}^d \times [0,\lambda]$, and we define $$\eta= \frac{1}{\lambda}\sum_{(x,u) \in \eta}\delta_x.$$
We define $(\eta^{\varepsilon, \theta, \lambda}_t)_{t \geq 0}$ to be the (unique?) solution to the Martingale Problem with initial condition $\eta_0$ and generator $A_{\varepsilon, \theta, \lambda}$ that satisfies
\begin{eqnarray}\label{Eq: Prelimit Lookdown Generator}
&&A_{\epsilon, \theta, \lambda}f(\eta ) \\
&&\quad =f(\eta )\,\sum_{(x,u)\in\eta}\,2 \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(x, \eta)\Bigg\{ \frac 12 \lambda^{-1}\int_u^{
\lambda}g(x,v_1)dv_1\times \frac { \theta\int_{\mathbb{R}^d}(g(y,u)-g(x,u))q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\bar{
\eta },dy)}{g(x,u)}\non\\
&&\qquad\qquad\qquad\qquad\qquad\qquad\qquad +\lambda^{-1}\theta\int_u^{
\lambda}\int_{\mathbb{R}^d}\left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\eta,dy)dv_1\nonumber\Bigg\}\\
&&\qquad\qquad
+f(\eta )\sum_{(x,u)\in\eta}\,\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(x,\eta) u^2 -b_{\varepsilon,\theta, \lambda}(x,\eta)u\right)\frac {\partial_u g(x,u)}{g(x,u)}.\nonumber
\end{eqnarray}
for all smooth functions $f \in C(\mathbb{R}^d)$. 
\end{definition}
In \S \ref{sec: Markov Mapping Theorem application}, through an application of the Markov Mapping Theorem, we will show that the spatial projection of $(\eta^{\varepsilon, \theta, \lambda}_t)_{t \geq 0}$ has the same distribution as $(\eta^{\varepsilon, \theta, N}_t)_{t \geq 0}$ if we take $\lambda = N$. Specifically, we mean that when $\lambda=N$, 
$$(\eta^{\varepsilon,\theta, \lambda}(t))_{t \geq 0}:=\left(\frac{1}{\lambda}\sum\limits_{\substack{(X(t),U(t))\in \eta^{\varepsilon,\theta, \lambda}(t) \\ U(t) < \lambda}} \delta_{X(t)}\right)_{t \geq 0}$$
has the same distribution (as stochastic processes) as $(\eta^{\theta}_t)_{t \geq 0}$ in Definition \ref{Def: Rescaled Models}. As a result, we use the same notation $\eta$ to denote these two essentially identical processes which take values in the space of empirical measures. On the other hand, we reserve the notation $\eta$ strictly for the spatial-level process.\\~\\ Furthermore, the application of Markov Mapping Theorem implies that particle levels are, conditional on $\eta$, i.i.d and uniformly distributed between $[0, \lambda]$.  Theorem A.10 in \cite{kurtz/rodrigues:2011} states that convergence of $(\eta^{\varepsilon, \theta, \lambda}_t)_{t \geq 0}$ to a conditionally Poisson system $(\xi_t)_{t \geq 0}$ with Cox measure $\Xi_t \times \Lambda$ is equivalent to convergence of $(\eta^{\varepsilon, \theta, N}_t)_{t \geq 0}$ to $(\Xi_t)_{t \geq 0}$. As a result, it suffices for us to focus on tightness of $(\eta^{\varepsilon, \theta, \lambda}_t)_{t \geq 0}$ and spatial convergence of $(\eta^{\varepsilon, \theta, N}_t)_{t \geq 0}$ as $\theta \to \infty$.

@@

    U_{\tau+s}(\tau+s)=U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))}.

>>>>

\begin{definition}[Model parameterization and assumptions]
    \label{def:model_setup}
    For each $\theta \ge 0$,
    let $\left(\eta^\theta(t)\right)_{t \ge 0}$
    be the continuous-time measure-valued Markov process described above
    with birth rates, establishment probabilities, and death rates
    determined as follows.
    Suppose $\gamma(x, m)$, $r(x, m)$, and $F(x, m)$
    are bounded, uniformly continuous functions
    from $\IR^d \times \IR_{\ge 0}$ to $\IR_{\ge 0}$.
    Furthermore, suppose $r$ takes values in $[0, 1]$
    and has uniformly bounded second derivatives,
    and that $(x, m) \mapsto m^2 \gamma(x, m)$ is unformly bounded.
    Fix nonnegative values $\epsilon_r$, $\epsilon_\gamma$, and $\epsilon_F$,
    with $\epsilon_r < \epsilon_\gamma - 1/\theta$.
    Suppose $F: \IR^d \times \IR_{\ge 0} \to \IR$ is bounded and uniformly continous
    and define
    \begin{align}
        \mu(x, \eta)
        =
        r(x, \smooth{r} \eta(x))
        \gamma(\smooth{\gamma} \eta(x))
        - \frac{1}{\theta}
        F(x, \smooth{F} \eta(x)) .
    \end{align}
    Let $N$ be a positive number determined by $\theta$.
    When the state of the process is $\eta$,
    offspring of mass $1/N$ are produced at location $x$
    with rate $\theta \gamma(x, \smooth{\gamma} \eta^{\theta}(x)) N \eta^{\theta}_s(dx)$
    and adults die at location $x$ with rate $\theta \mu(x, \eta) N \eta^{\theta}_s(dx)$,
    (i.e., at rates $\theta \gamma$ and $\theta \mu$ per capita respectively).
    Offspring disperse to a location offset from the parent's location
    by an independent Gaussian with mean $\meanq/\theta$
    and covariance matrix $\covq / \theta$;
    an offspring at $x$ establishes instantaneously
    with probability $r(x, \smooth{r} \eta^{\theta}(x))$, or else dies.
\end{definition}

@@

\paragraph{Remark:}
An equivalent way to describe the model
would be to say that an individual at $x$ gives birth at rate
$$
    \gamma(x, \smooth{\gamma} \eta(x))
    \int r(x, \smooth{r} \eta(y)) q(x, dy) ,
$$
and that offspring disperse according to the kernel
$$
    q_\theta^\mathfrak{m}(x, dy)
    :=
    \frac{
        r(y, \smooth{r} \eta(y)) q_\theta(x, dy)
    }{
        \int r(x, \smooth{r} \eta(z)) q_\theta(x, dz)
    } .
$$
Clearly, the random walk driven by this dispersal kernel
should be biased towards regions of higher establishment probability.
For comparison to future results,
it is interesting to write down the limiting generator:
\begin{align*}
    \lim_{\theta \to \infty}
    \theta \int (f(y) - f(x)) q_\theta^\mathfrak{m}(x, dy)
    &=
    \frac{
        \DG\left[ f(\cdot) r(\cdot, \smooth{r} \eta(\cdot)) \right](x)
        - 
        f(\cdot) \DG\left[ r(\cdot, \smooth{r} \eta(\cdot)) \right](x)
    }{
        r(x, \smooth{r} \eta^{\theta}(x))
    } .
\end{align*}
In the simplest case of unbiased, isotropic dispersal,
$\meanq = 0$ and $\covq = I$, so $\DG = \Delta$,
and this is equal to
\begin{align*}
    \Delta f(x) + 2 \grad f(x) \cdot \grad \log r(\cdot, \smooth{r} \eta(\cdot))(x) .
\end{align*}
However, we will see that following a lineage back through the population
has a different behavior yet again.

@@

    The sequence of stochastic processes
    $(\eta^\theta_t)_{t \geq 0}$
    converges along subsequences in distribution as $\theta \to \infty$
    to a measure-valued process $(\eta_t)_{t \geq 0}$
    which satisfies that, for every $f:\mathbb{R}^d \rightarrow \mathbb{R}$,
    \begin{align} \label{eqn:mgale_problem}
        M_t
        &:=
        \langle f(x), \eta_t(dx) \rangle
        -
        \langle f(x), \eta_0(dx) \rangle
        \\ & \qquad
        -
        \int_0^t \big\langle
            \gamma(x, \smooth{\gamma} \eta_{s}(x))
            \mathcal{B}\left(
                f(\cdot) r(\cdot, \smooth{r} \eta_{s}(\cdot))
            \right)(x)
            +
            f(x)
            F(x, \smooth{F} \eta_{s}(x)),
            \eta_{s}(dx)
        \big\rangle ds,
    \end{align}
    is a martingale.
    The quadratic variation of $M_t$ is given by 
    \begin{align} \label{eqn:mgale_variation}
        [ M ]_t
        =
        \delta
        \int_0^t
        \big\langle
            \gamma\left( x, \smooth{\gamma} \eta_{s}(x) \right)
            r\left(x, \smooth{r} \eta_{s}(x) \right)
            f^2(x),
            \eta_{s} (dx)
        \big\rangle ds. 
    \end{align}
    In other words, the limit is a measure-valued process with non-local interactions.
    Furthermore, if $\delta = 0$ the limit is deterministic.
\end{theorem}

@@

We now write down the generator of
the population model with levels between $[0, \lambda]$.

We should consider an initial population of $O(\lambda)$ many particles with levels
uniformly distributed between $[0, \lambda]$.
We write $(\xi(t))_{t \geq 0}$
for our population.
To ensure we have bounded intensity, 
we scale the empirical distribution of particles with a factor of $1/\lambda$,
so we write
$$\eta_t:=\frac{1}{\lambda}\xi_t(\cdot \times [0,\lambda])=
\frac{1}{\lambda}\sum\limits_{\substack{(X(t),U(t))\in \xi \\ U(t) < \lambda}} \delta_{X(t)}.$$

From here onwards,
we write $\xi$ to be the particle systems with levels,
while $\eta$ is the normalised empirical distribution.
An individual in the spatial population $\eta$ living at spatial location $x$
produces one adult offspring at rate $\gamma^{\mathfrak{m}}(x, \eta)$, where
$$\gamma^{\mathfrak{m}}(x,\eta)=\gamma(x,\eta) \int r (y, \eta)q(x,dy),$$
where $q(x,dy)$ is the dispersion kernel.

Recall that we only track the adult population; maturity, if achieved, is instantaneous.
The location of this adult offspring is given by
the distribution 
\[ q^{\mathfrak{m}}(x,\eta,dy) = \frac{r(y,\eta) q(x,dy)}{\int_{\mathbb{R}^d} r(y,\eta) q(x,dy)}. \]

In the lookdown version of our model,
the individual $(x,u)\in \xi$
gives birth to an offspring at rate 
$2(\lambda-u)\lambda^{-1} \gamma^{\mathfrak{m}}(x, \eta)$. 
(Averaging over the distribution of the
level $u$,
we recover $\gamma^{\mathfrak{m}}(x, \eta)$.)

@@

Evidently this mechanism increases the proportion
of individuals with higher levels.
To restore the property that,
conditional on $\eta$,
the intensity of levels is conditionally uniform,
we impose that 
the level associated with $(x,u)\in\eta$
evolves according to the differential equation
$$\dot{v}=  \gamma^{\mathfrak{m}}(x, \eta) 
\left\{\lambda^{-1}(\lambda -v)^{2}
-(\lambda -v)\right\}.$$

See~\cite{etheridge/kurtz:2018}, Section~3.4 for a detailed explanation.
In order to incorporate death,
the level of the individual $(x,u)\in \eta$ 
moves upwards at an additional rate
$ \mu(x,\eta)$
(on reaching level $\lambda$
an individual is deemed to have died).
Overall, we assume that
the level associated with $(x,u)\in\eta$
evolves according to
$$\dot{u}= \gamma^{\mathfrak{m}}(x, \eta) 
\left\{\lambda^{-1}(\lambda -u)^{2}
-(\lambda -u)\right\}+\mu(x,\eta)u.$$
We shall write 
$$b(x,\eta):= \big\{\gamma^{\mathfrak{m}}(x,\eta)
-\mu(x,\eta)\big\}$$
to be the local branching rate.
Note that this quantity captures
the deviation from criticality
in the branching mechanism.
In this notation,
the differential equation 
governing the level of the individual $(x,u)\in\eta$ is
\begin{align}
\dot{u}&=\lambda  \gamma^{\mathfrak{m}}(x,\eta) 
\left\{\left(1-\frac{u}{\lambda}\right)^{2}
-1 +2\frac{u}{\lambda}\right\} -b(x,\eta)u \nonumber \\
&=\lambda^{-1}  \gamma^{\mathfrak{m}}(x,\eta) u^2 -b(x,\eta)u. \label{differential equation for level}
\end{align}
In this setting, the generator of our model
acting on the test functions $f(\xi)=\prod_{(x,u) \in \xi}g(x,u)$
satisfies
%We assume that  locations in ${\mathbb{ R}}^d$.

\begin{eqnarray}\label{Generator of prelimit simplest model}
&&Af(\xi ) \nonumber \\
&&\quad =f(\xi )\,\sum_{(x,u)\in\xi}\,2\lambda^{-1} \gamma^{\mathfrak{m}}(x, \eta)
\int_u^{
\lambda}\Bigg(\frac 12\frac {\int_{\mathbb{R}^d}g(y,u)q^{\mathfrak{m}}(x,\eta,d
y)g(x,v_1)}{g(x,u)} \label{multgen3}\\
&&\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad
+\frac 12\int_{\mathbb{R}^d}g(y,v_1)q^{\mathfrak{m}}(x,\eta ,dy)-
1\Bigg)dv_1\nonumber\\
&&\quad \quad +f(\eta )\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}(x,\eta) u^2 -b(x,\eta)u\right)\frac {\partial_u g(x,u)}{g(x,u)}\nonumber\\
&&\quad =f(\eta )\,\sum_{(x,u)\in\eta}\,2 \gamma^{\mathfrak{m}}(x, \eta)\lambda^{-1}\int_u^{
\lambda}\Bigg(\frac 12\frac {\theta\int_{\mathbb{R}^d}(g(y,u)-g(x,u))q^{\mathfrak{m}}(x,\eta,dy)g(x,v_1)}{g(x,u)}\non\\
&&\qquad\qquad\qquad\qquad\qquad\qquad\qquad +\theta\int_{\mathbb{R}^d}\left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}(x,\eta,dy)\Bigg)dv_1\nonumber\\
&&\qquad\qquad
+f(\eta )\sum_{(x,u)\in\eta}\,\left(\lambda^{-1} \gamma^{\mathfrak{m}}(x,\eta) u^2 -b(x,\eta)u\right)\frac {\partial_u g(x,u)}{g(x,u)}.\nonumber
\end{eqnarray}
The two terms under the integral correspond, respectively,
to the parent being assigned a level other than $u$,
and being reallocated to the level $u$
during a birth event.
In the first case, the parent at location $x$,
which had level $u$ before the event,
moves to level $v_1$,
and the child is inserted at level $u$
and location $y$;
in the second the parent retains its level,
and offspring is inserted at level $v_1$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{Scaling of the Pre-limit Lookdown Model}

To scale our lookdown model to be consistent with
the spatial model described in \S \ref{sec: Model and main results},
we will let $\lambda$ takes on the role of $N$
in \S \ref{sec: Model and main results},
i.e. each individual has mass $1/\lambda$
in the scaling limit.
Time is once again scaled by $\theta$,
and the birth, death and establishment rates 
depend on local densities given by
mollification over Gaussian kernels with radius
$\varepsilon_{\gamma}$, $\varepsilon_{F}$ and $\varepsilon_{r}$.

Explicitly, in the $\theta$-th stage of re-scaling,
an individual has mass $\frac{1}{\lambda} := \frac{1}{N}$
and a level between $[0,N]$;
the established birth rate $\gamma(x,\eta)$ is
$$\theta\gamma^{\mathfrak{m}}_{\theta}(x, \eta):=~\theta\gamma(x, \varrho_{\gamma}*\eta(x)) \int r(y, \varrho_{r}*\eta(y))q_{\theta}(x,dy);$$
the local branching mechanism $b(x,\eta)$ is 
$$b_{\theta}(x, \eta):=~ \theta \bigg\{ \gamma(x, \varrho_{\gamma}*\eta(x)) \int r(y, \varrho_{r}*\eta(y))q_{\theta}(x,dy)-\mu(x, \eta)\bigg\};$$
and the dispersal kernel $q^{\mathfrak{m}}(x,dy)$ is 
$$q^{\mathfrak{m}}_{\theta}(x,\eta,dy) :=~ \frac{r(y,\varrho_{r}*\eta(y)) q_{\theta}(x,dy)}{\int_{\mathbb{R}^d} r(y,\varrho_{r}*\eta(y)) q_{\theta}(x,dy)}.$$

We can now define our pre-limit explicitly as a solution to a Martingale Problem.
\begin{definition}[Martingale Problem Characterisation]
\label{Def: Rescaled Lookdown Models}

For test measures $\xi$ taking value in $\mathcal{M}_F(\mathbb{R}^d \times [0,N])$,
the set of finite measures on $\mathbb{R}^d \times [0,N]$,
we define
$$\eta:= \frac{1}{N}\xi(\cdot  \times [0, N])=
\frac{1}{N}\sum_{(x,u) \in \xi}\delta_x$$
to be its re-scaled spatial projection.

We define $(\xi^{\theta}_t)_{t \geq 0}$
to be the (unique) solution
to the Martingale Problem
with initial condition $\xi_0$
and generator $A^{\theta}$ that satisfies

\begin{eqnarray}\label{Eq: Prelimit Lookdown Generator}
&&A^{\theta}f(\xi ) \\
&&\quad =f(\xi )\,\sum_{(x,u)\in\eta}\,2 \gamma^{\mathfrak{m}}_{\theta}(x, \eta)\Bigg\{ \frac 12 \lambda^{-1}\int_u^{
\lambda}g(x,v_1)dv_1\times \frac { \theta\int_{\mathbb{R}^d}(g(y,u)-g(x,u))q^{\mathfrak{m}}_{\theta}(x,\eta,dy) }{g(x,u)}\non\\
&&\qquad\qquad\qquad\qquad\qquad\qquad\qquad +\lambda^{-1}\theta\int_u^{
\lambda}\int_{\mathbb{R}^d}\left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\theta}(x,\eta,dy)dv_1\nonumber\Bigg\}\\
&&\qquad\qquad
+f(\eta )\sum_{(x,u)\in\xi}\,\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\eta) u^2 -b_{\theta}(x,\eta)u\right)\frac {\partial_u g(x,u)}{g(x,u)}.\nonumber
\end{eqnarray}
for all smooth functions $f \in C^{2}_{0}(\mathbb{R}^d)$. 
\end{definition}

In \S \ref{sec: Markov Mapping Theorem Application},
applying Markov Mapping Theorem,
we will show that the spatial projection of $(\eta^{\theta}_t)_{t \geq 0}$ has the same distribution as $(\eta^{\varepsilon, \theta, N}_t)_{t \geq 0}$ if we take $\lambda = N$. Specifically, we mean that when $\lambda=N$, 
$$(\eta^{\theta}(t))_{t \geq 0}:=\left(\frac{1}{\lambda}\sum\limits_{\substack{(X(t),U(t))\in \eta^{\theta}(t) \\ U(t) < \lambda}} \delta_{X(t)}\right)_{t \geq 0}$$
has the same distribution (as stochastic processes) as $(\eta^{\theta}_t)_{t \geq 0}$ in Definition \ref{Def: Rescaled Models}. As a result, we use the same notation $\eta$ to denote these two essentially identical processes which take values in the space of empirical measures. On the other hand, we reserve the notation $\eta$ strictly for the spatial-level process.\\~\\ Furthermore, the application of Markov Mapping Theorem implies that particle levels are, conditional on $\eta$, i.i.d and uniformly distributed between $[0, \lambda]$.  Theorem A.10 in \cite{kurtz/rodrigues:2011} states that convergence of $(\eta^{\theta}_t)_{t \geq 0}$ to a conditionally Poisson system $(\xi_t)_{t \geq 0}$ with Cox measure $\Xi_t \times \Lambda$ is equivalent to convergence of $(\eta^{\varepsilon, \theta, N}_t)_{t \geq 0}$ to $(\Xi_t)_{t \geq 0}$. As a result, it suffices for us to focus on tightness of $(\eta^{\theta}_t)_{t \geq 0}$ and spatial convergence of $(\eta^{\varepsilon, \theta, N}_t)_{t \geq 0}$ as $\theta \to \infty$.

@@

    U_{\tau+s}(\tau+s)=U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))}.
